
\section{Experimental Setup}\label{sec:taseh} 
The detector of TASEH is located at the Department of Physics, National 
Central University, Taiwan and housed within a cryogen-free dilution 
refrigerator (DR) from BlueFors. An 8-Tesla superconducting solenoid 
with a 
bore diameter of 76~mm and a length of 240 mm is integrated with the DR. 

The data for the analysis presented in this paper were collected by TASEH 
from October 13, 2021 to November 15, 2021, and termed as the CD102 data, 
where CD stands for ``cool down''. 
During the data taking, the cavity sat in the center of the magnet bore 
and was connected via holders to the mixing flange of the DR at a 
temperature of $T_{\rm mx}\simeq27$~mK. 
The temperature of the cavity stayed at $T_\text{c}\simeq155$~mK, higher 
with respect to the 
DR; it is believed that the cavity had an unexpected thermal contact with the 
radiation shield in the DR. 
The cavity, made of oxygen-free high-conductivity (OFHC) copper, has an 
effective volume of 0.234~L and is a two-cell cylinder split along 
the axial direction. 
The cylindrical cavity has an inner radius of 2.5~cm and a 
height of 12~cm.  In order to maintain a smooth surface, the cavity underwent 
the processes of annealing, polishing, and chemical cleaning. The resonant 
frequency of the TM$_{010}$ mode at the cryogenic temperature 
can be tuned over the range of 
%4.717--4.999~GHz via the rotation of an off-axis OFHC copper tuning rod, from 
4.667--4.959~GHz via the rotation of an off-axis OFHC copper tuning rod, from 
the position closer to the cavity wall to the position closer to the cavity 
center (i.e. when the vector from the rotation axis to the tuning rod is 
at an angle of $0^\circ$ to $180^\circ$, with respect to the vector from the 
cavity center to the rotation axis). 
%
Over the frequency range of the CD102 run, the form factor $C_{010}$ as 
defined in Eq.~\eqref{eq:formfactor} varies from 0.60 to 0.61 and 
%0.598 to 0.613 and  
the intrinsic, unloaded quality factor $Q_0$ at the cryogenic temperature 
($T_\mathrm{c}\simeq 155$~mK) is $\simeq 60700$. 
The values of $C_{010}$ are derived from the magnetic field map provided by 
BlueFors and the cavity electric field distribution simulated with 
 Ansys HFSS (high-frequency structure simulator).  

An output probe, made of a 50-$\Omega$ semi-rigid coaxial cable that was 
soldered to an SMA (SubMiniature version A) connector, was inserted into the 
cavity and its depth was set for 
$\beta\simeq2$; the optimization of the value of $\beta$
is discussed in more detail in Ref.~\cite{TASEHInstrumentation}. 
  The signal from the output probe was directed to an 
impedance-matched amplification chain. The first-stage amplifier was 
a low noise high-electron-mobility transistor (HEMT) amplifier with an 
effective noise temperature of $\approx 2$~K, mounted on the 4K flange. 
The signal was further amplified at room temperature via a 
three-stage post-amplifier, and down-converted 
and demodulated to in-phase (I) and quadrature (Q) components and digitized 
by an analog-to-digital converter with a sampling rate of 2~MHz. 
%The frequency resolution of the spectra was 1~kHz.

The CD102 data cover the frequency range of \flo--\fhi~GHz. In this paper, most
 of the frequencies in unit of GHz are quoted with five decimal places as the 
absolute accuracy of frequency is $\approx 10$~kHz. It shall be noted that the 
frequency resolution is 1~kHz.  
There were 837 resonant-frequency steps in total, with a frequency difference 
of $\Delta f_\text{s}=95-115$~kHz between the steps. 
The value of $\Delta f_\text{s}$ was kept within 10\% of 
the nominal value 105~kHz ($\lesssim$ half of the cavity 
line width), rather than 
a fixed value, such that the rotation angle of the tuning rod did not need to 
be fine-tuned and the operation time could be minimized. A 10\% variation of 
the $\Delta f_\text{s}$ is found to have no impact on the \gagg\ limits. 
Each resonant-frequency step is denoted as a ``scan'' 
and the data integration time was about 32-42 minutes. The integration 
time was determined based on the target \gagg\ limits and the experimental 
parameters in Table~\ref{tab:tasehbenchmark}; the variation of the integration 
time aimed to remove the frequency-dependence in the \gagg\ limits caused by   
frequency dependence of the added noise \ta. 

A more detailed description of the TASEH detector, the operation of the 
data run, and the calibration of the gain and added noise temperature of the 
whole amplification chain can be found in Ref.~\cite{TASEHInstrumentation}. 
See Table~\ref{tab:tasehbenchmark} for the benchmark experimental parameters 
that can be used to estimate the sensitivity of TASEH. 

\begin{table}
\caption{The benchmark experimental parameters for estimating the sensitivity 
of TASEH. The definitions of the parameters can be found in Sec.~\ref{sec:intro}. 
More details regarding the determination and the measurements of 
some of the parameters may be found in Ref.~\cite{TASEHInstrumentation}.} 
\label{tab:tasehbenchmark}
\begin{center}
\begin{tabular}{cr}
\hline\hline
 $f_\mathrm{lo}$ & \flo~GHz\\
 $f_\mathrm{hi}$ & \fhi~GHz \\
% $N_\text{step}$ & 839 \\
 $N_\text{step}$ & 837 \\
 $\Delta f_\text{s}$ & 95 -- 115 kHz \\
% $f_\text{resolution}$ & 1 kHz \\
 $B_0$  & 8 Tesla \\
 $V$ & 0.234 L \\ %234255~mm$^3$ 
% $C_{010}$ & 0.598 -- 0.613 \\
 $C_{010}$ & 0.60 -- 0.61 \\
 $Q_0$ & 58000 -- 65000 \\
 $\beta$ & 1.9 -- 2.3 \\
 $T_{\rm mx}$ & 27--28~mK\\
 $T_\mathrm{c}$ & 155~mK \\
 \ta & \noise~K \\
 $\Delta f_a$ & 5 kHz \\
\hline\hline
\end{tabular}
\end{center}
\end{table}
